### 2020-12-21 docs/submission/srep/coverletter/letter-tex/covlet.tex
polishes docs/submission/srep/coverletter/letter-tex/covlet.tex

%* A brief explanation of why the work is appropriate for Scientific Reports
We selected Scientific Reports for 
its reputation on publishing works that are algigment to the principles of reproducibility and open science. 
as well as the various topics and readers in areas of natural and clinical science that our work can be reached. 
Paper is containing original research and has not been submitted or published earlier 
in any journal and is not being considered for publication elsewhere. 
All authors have seen and approved the manuscript and have contributed significantly for the paper.

%* The names and contact information of any reviewers you consider suitable
%* The names of any referees you would like excluded from reviewing
Two potential reviewers that we consider suitable for our work can be:
Bedartha Goswami, bedartha.goswami@uni-tuebingen.de,
at University of Tübingen investigating nonlinear time series analysis; recurrence plots, and
Serhiy Yanchuk, yanchuk@math.tu-berlin.de, at Technical University of Berlin investigating 
dynamics time delay networks of dynamical systems; pattern formation; coupled systems.

>>>>

%* A brief explanation of why the work is appropriate for Scientific Reports
Our work is appropriate to be considered to be published in Scientific Reports due to
its alignment to the principles of open science (e.g., reproducibility, transparency, reusability and open accessibility).
Similarly, we chosen Scientific Reports because of the outcomes of our work might lead to 
potential applications in areas of natural and clinical science.
Our manuscript is containing original research and has not been submitted or published earlier 
in any journal and is not being considered for publication elsewhere. 
Authors have seen and approved the manuscript and have contributed significantly to it.

%* The names and contact information of any reviewers you consider suitable
%* The names of any referees you would like excluded from reviewing
Finally, two potential reviewers for our work can be:
Bedartha Goswami, bedartha.goswami@uni-tuebingen.de,
at University of Tübingen investigating nonlinear time series analysis; recurrence plots, and
Serhiy Yanchuk, yanchuk@math.tu-berlin.de, at Technical University of Berlin investigating 
dynamics time delay networks of dynamical systems; pattern formation; coupled systems.
